A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-25 0_main.tex
MAT distance remapping and the cutoff point for markings
restructure method and give a clear overview
add experimentation sections
big refactor of method
new underline and textcolor macros
rename sections;  section -> subsection etc.
describe tick placement algorithms
add conclusion and future work
add discussion section
rewrite method overview
rewrite transitioning section
intial abstract

@@

@@

@@

%    \newcommand{\todo}[1]{\hl{#1}}

%	\newcommand{\temp}[1]{\textcolor[rgb]{0, 0, 0.2}{#1}}
%	\newcommand{\tim}[1]{\temp{\todo{[Tim: #1]}}}
%	\newcommand{\jun}[1]{\temp{\todo{[Jun: #1]}}}
%	\newcommand{\charlie}[1]{\textcolor[rgb]{0, 0.2, 0}{\todo{[Charlie: #1]}}}
%	\newcommand{\toberemoved}[1]{\textcolor[rgb]{0.9, 0, 0.2}{\st{#1}}}
%	\newcommand{\inserttext}[1]{\textcolor[rgb]{0, 0.7, 0}{\hl{#1}}}
%	\newcommand{\replacewith}[2]{\toberemoved{#1}\inserttext{#2}}

    \newcommand{\changed}[1]{#1}
    %\newcommand{\changed}[1]{\hl{#1}}

@@

\title{Title}

\author{Paper ID: xxx}

@@

\begin{abstract}
abstract
\end{abstract}

@@

% \temp{Table of contents just for reviewing purposes
% \tableofcontents
% }

@@

@@

>>>>

	\newcommand{\degree}{^\circ}

@@

	\DeclareMathOperator*{\argmax}{arg\,max}
	\DeclareMathOperator*{\argmin}{arg\,min}

	\DeclareMathOperator{\abs}{abs} % absolute function

@@

	\usepackage{listings} % for listing C++ code instead of pseudocode
	\lstset{ 
      breaklines=true,                 % sets automatic line breaking
    }

	\newcommand{\wmin}{w_\text{min}}
	\newcommand{\wmax}{w_\text{max}}
	\newcommand{\wout}{w_\text{out}}
	\newcommand{\win}{w_\text{in}}

@@

    \newcommand{\todo}[1]{\hl{#1}}

	\newcommand{\temp}[1]{\textcolor[rgb]{0, 0, 0.2}{#1}}
	\newcommand{\tim}[1]{\temp{\todo{[Tim: #1]}}}
	\newcommand{\jun}[1]{\temp{\todo{[Jun: #1]}}}

	\newcommand{\old}[1]{\textcolor{gray}{#1}}

	\setulcolor{red}

	\usepackage[normalem]{ulem} % squigly underline

@@

\title{A robust framework for variable extrusion width concentric toolpath generation}

%\author{Paper ID: xxx}

@@

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) works by depositing material along paths which lie in horizontal layers.
The outlines of each layer are filled (partly) using contour-following toolpaths approximately the size of the printing nozzle.
Filling the outlines with extruded material densely and accurately is important for fabricating parts accurately and stiffly.
Especially thin parts require an accurate dense filling, such as casings for electronics, blowmolding prototypes, (architectural) models and some tpyes of microstructure.

A naive strategy for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a constant width.
In the center of the outline shapes this naive strategy can result in underfill regions and overfill regions as wide as the nozzle size.
Some previous literature solves these overfill and underfill problems by locally extruding a small amount of material less or more.
However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size.
We propose a framework which allows to define beading strategies which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.

Our method determines the number of extrusion beads at each location, then it generates the beads from the center of the outline shape outward and finally connects all bead together to form extrusion toolpaths.
We determine the middle of the shape by applying a significance measure to the skeleton of the outline polygon, use the beading strategy to determine the optimal number of beads in those middle regions and derive the toolpath locations as distances from the middle parts of the skeleton from the beading strategy.
Because the skeletal structure decomposes the outline domain into simple cells, the toolpaths can be generated by drawing straight line segments along each cell.

Our framework is shown to be able to emulate several methods discussed in related literature and it enables a wide range of other beading strategies.
We show that we can define a strategy which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
We show that our implementation exhibits computation times in the same order of magnitude as the naive method.
\end{abstract}

@@

 \temp{%Table of contents just for reviewing purposes
 \tableofcontents
 }

@@

\input{6_validation}

\input{8_discussion}

@@

\input{12_conclusions_future_work}
